% Andrew Clunis' CV, LaTeX format.

% lots of help shamelessly taken from:
% http://www.cv-templates.info/2009/03/professional-cv-latex/

% Build with `xelatex cv.tex`.  You'll need texlive

\documentclass[letterpaper,10pt]{article}

%A Few Useful Packages
\usepackage{marvosym}
\usepackage{fontspec}                                   %for loading fonts
\usepackage{setspace}
\usepackage{xunicode,xltxtra,url,parskip}       %other packages for formatting
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}

% an alternative to Layaureo can be ** \usepackage{fullpage} **
\usepackage{fullpage}
\usepackage{supertabular}                               %for Grades
\usepackage{longtable}
\usepackage{titlesec}                                   %custom \section

%Setup hyperref package, and colours for links
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

%FONTS
\defaultfontfeatures{Mapping=tex-text}
\setmainfont[SmallCapsFont = Fontin SmallCaps]{Fontin}

%CV Sections inspired by:
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{3pt}
\titleformat{\subsection}{\Large}{}{0em}{}
\titlespacing{\subsection}{1pt}{5pt}{5pt}
%Tweak a bit the top margin
%\addtolength{\voffset}{-1.3cm}

\begin{document}

\pagestyle{empty} % non-numbered pages

\par{\centering
{\Huge Andrew \textsc Clunis
}\bigskip\par}

\section{Personal}
\begin{longtable}{p{3cm}|p{12cm}}
  \textsc{Date of Birth:} & July 29th, 1985 \\
  \textsc{Address:} & 305-457 McLeod St, Ottawa, Ontario, Canada \\
  \textsc{Phone:} & +1.613.286.8829 \\
  \textsc{Web:} &  \href{http://www.orospakr.ca/}{http://www.orospakr.ca/} \\
  \textsc{Twitter and G+:} & \href{http://twitter.com/orospakr}{@orospakr} \emph{and} \href{https://plus.google.com/101728978406554574081}{+Andrew Clunis}\\
  \textsc{GitHub:} & \href{https://github.com/orospakr}{https://www.github.com/orospakr} \\
  \textsc{Electronic Mail:} & \href{mailto:andrew@orospakr.ca}{andrew@orospakr.ca} \\
\end{longtable}

\section{Overview}
I am a software developer, with emphasis on open source and agile
approaches, with experience writing both desktop, mobile, server, and
even a few rich web applications.  As an active participant in the
Free Software and Linux communities, I've contributed code to and
created a number of different projects.  I'm something of a generalist
and have interests, expertise, and experience distributed throughout
multiple phyla of the software ecosystem.

\section{Environments}
\begin{longtable}{p{3cm}|p{12cm}}
  \textsc{Languages} & Ruby, JavaScript, Python, C(++), C\#, Java, and ObjC \\
  \multicolumn{2}{c}{} \\
  \textsc{Operating Systems} & GNU/Linux (Debian/Ubuntu), *BSD, Android, OS X, and Windows\\
  \multicolumn{2}{c}{} \\
  \textsc{Platforms} & GTK, Gstreamer, Rails, Android (and Android internals), Mono, Node.js, iOS, .net MVC, Xamarin's MonoDroid and MonoTouch, and the Linux kernel
\end{longtable}

\section{Engagements and Projects}
\footnotesize{If a project was part of a larger engagement, it is noted in small text on the left.}
\begin{longtable}{p{3cm}|p{12cm}}
  \emph{Current} & Maker and Founding Board Member \emph{at} \textsc{CREDIL} \\
  \textsc{September 2008} & \footnotesize{Participated in the founding of the organisation, implemented technical solutions using Free Software (detailed below) for multiple organisations as a part of CREDIL teams.  Continuing to serve as board member.} \\
\multicolumn{2}{c}{} \\
  \textsc{Jan 2012-Oct 2012} & Software Developer \emph{for} \textsc{Macadamian Technologies Inc.} \\
   & \footnotesize{Worked on two customer projects (Samsung and RIM, detailed below), and internal research projects regarding new platforms (namely Xamarin MonoDroid/MonoTouch and Windows Metro).} \\
\multicolumn{2}{c}{} \\
  \textsc{Mar 2012-Jun 2012} & Software Developer \emph{for} \textsc{Samsung} \emph{via} \textsc{Macadamian} \\
  \tiny{Macadamian} & \emph{Android Frontend for a Prototype Mobile Edge Networking System on Android} \\
   & \footnotesize{Implemented application-specific protocol at layer 6, application UI navigation regime, and other UI components.  As team member most experienced with git, assisted others routinely.  Used Android and Java.} \\
\multicolumn{2}{c}{} \\
  \textsc{Jun 2012-Oct 2012} & Software Developer \emph{for} \textsc{Research in Motion} \emph{via} \textsc{Macadamian} \\
  \tiny{Macadamian} & \emph{Platform Demonstration Application} \\
   & \footnotesize{Designed and implemented backend REST content service and BlackBerry 10 mobile app client interface bindings.  Used C++, QNX, QtCore, C\#, .net MVC 4, and BB10 Cascades.} \\
\pagebreak
\multicolumn{2}{c}{} \\
  \textsc{Nov 2010-Jul 2011} & Software Developer \emph{for} \textsc{HRSDC} \\
  \tiny{CREDIL} & \emph{Video Stream ``Reflector'' for IITB Webcasting System} \\
   & \footnotesize{Implemented ``{\href{https://github.com/orospakr/stream-pump}{Stream Pump}}'', a thin MMSH video stream proxy for delivering of live video to large numbers of desktops behind network bottlenecks in lieu of \mbox{layer 3} \mbox{multicast}.  Used Node.js and GNU/Linux.} \\
\multicolumn{2}{c}{} \\
  \textsc{Summer 2011} & Software Developer \emph{for} \textsc{Language Technologies Research Centre (CRTL)} \\
  \tiny{CREDIL} & \emph{Remote Desktop Access Customer Portal} \\
   & \footnotesize{Bootstrapped customer portal and authentication facilities.  Specified requirements for and integrated designer-produced layout and visual design assets.  Used Rails 3 and PostgreSQL.} \\
  \multicolumn{2}{c}{} \\
  \textsc{Sept 2008-Dec 2011} & Software Developer \emph{for} \textsc{NovaVision} \\
  \tiny{CREDIL} & \emph{Retail Ambient Music and Digital Signage System} \\
   & \footnotesize{Implemented administration UI, REST interface, playlisting control, audio playback, and display components.  Used GNU/Linux, Ruby, GTK, Gstreamer, Clutter, the MRI Ruby C API, pyusb, and Rails 2.  Ancillary work included implementing prototype.js-based REST client for browser RIA, and userspace driver for LCD display unit included in the hardware platform. System remains deployed for several large customers.} \\
  \multicolumn{2}{c}{} \\
  \textsc{Aug 2009-June 2010} & Software Developer \emph{for} OTGV-C \\
  \tiny{CREDIL} & \emph{SIP/h.264 Video Softphone Application for Android} \\
  & \footnotesize{Contributed to multiple components of the stack, including the streaming media engine and user experience.  Used Android, Java, C++, PJSIP, and OpenCore.} \\
  \multicolumn{2}{c}{} \\
  \textsc{Summer 2008} & Software Developer \emph{for} \textsc{Meloche Television} \\
  \tiny{CREDIL} & \emph{Presentation Display for Live Television Events} \\
   & \footnotesize{Implemented server and display components.  Used GNU/Linux, Ruby, GTK, and Ruby on Rails.  Developed for live industry television event hosted by a large pharmaceutical corporation.} \\
  %% END CREDIL PROJECTS %%
  \multicolumn{2}{}{} \\  
  \textsc{Apr 2007-Sept 2008} & Software Developer \emph{for} \textsc{Infoglobe} \\
   & \footnotesize{Supported existing television presentation system.  Developed recorder appliance system for use in legal procedings, using Python and Gstreamer.} \\
  \multicolumn{2}{c}{} \\
  \textsc{Winter 2006} & Drupal Developer \emph{for} \textsc{OpenConcept Consulting} \\
   & \footnotesize{Developed a solution to migrate web site content from an older proprietary CMS system to Drupal 5.} \\
  \multicolumn{2}{c}{} \\
  \textsc{Jul 2003-Jul 2006} & IT Administrator and Developer \emph{for} \textsc{Infoman Inc.} \\
   & \footnotesize{Maintained small office network, implemented a web application in Rails 1 for managing terms and definitions used in ISO JTC1 standardisation processes on e-business and e-learning.  Used GNU/Linux, PostgreSQL, and Ruby on Rails.} \\
  \multicolumn{2}{c}{} \\
  \textsc{2003-2008} & IT Administrator \emph{for} \textsc{Integral DX Engineering Ltd.} \\
   & \footnotesize{Provided incidental support and consulting on IT systems using Free Software for a growing mechanical engineering firm.} \\

\end{longtable}

\pagebreak

\section{Community and Open Source}
Contributed to or created the following projects:

\begin{longtable}{p{3cm}|p{12cm}}
  \textsc{\href{https://github.com/orospakr/stream-pump}{Stream Pump}} & MMSH Video Stream Reflector in Node.js \\
   & \footnotesize{Created new Free Software project to implement the HRSDC webcasting project detailed above.} \\
  \multicolumn{2}{c}{} \\
  \textsc{\href{https://github.com/orospakr/sharpify}{Sharpify}} & Strongly typed and asynchronous .NET adapter for Shopify's REST API \\
   & \footnotesize{Forked original \href{https://github.com/cmcdonaldca/shopify.net}{Shopify.net} project and added I/O asynchronocity and typing.} \\
  \multicolumn{2}{c}{} \\
  \textsc{\href{https://github.com/brownan/Minecraft-Overviewer}{Minecraft Overviewer}} & Minecraft to Google Maps JS API renderer \newline \footnotesize{Contributed sign live search box, allowing users to find places of note in a large Minecraft map quickly.} \\
  \multicolumn{2}{c}{} \\
  \textsc{\href{https://github.com/orospakr/ChesterSharp}{ChesterSharp}} & Access CouchDB asynchronously from C\# under both Mono and .net \newline \footnotesize{Implemented with Mono, HttpClient, and CouchDB.} \\
  \multicolumn{2}{c}{} \\
  \textsc{\href{http://www.gmusicbrowser.org}{gmusicbrowser}} & Media Player in Perl and GTK \\
   & \footnotesize{Contributed plugins, specifically for automatic song rating and an HTTP web interface and REST API.} \\
  \multicolumn{2}{c}{} \\
  \textsc{\href{https://github.com/orospakr/gmusicbrowser-remote}{GMB Remote}} & Remote Control App for Gmusicbrowser in C\# for both Android and iOS \\
   & \footnotesize{Created mostly as a demonstration of portable app development with the Xamarin Mono* platforms.} \\
  \multicolumn{2}{c}{} \\
  \textsc{\href{https://github.com/orospakr/rbclutter}{rbclutter}} & Ported rbclutter to Clutter 1.6 \\
   & \footnotesize{Ported rbclutter, a Ruby binding for the \href{https://live.gnome.org/Clutter}{Clutter} 3D user interface library, to Clutter version 1.6.} \\
  \multicolumn{2}{c}{} \\
  \textsc{\href{https://github.com/orospakr/tukia}{Tukia}} & Controlled Vocabulary Management Tool for ISO standardization processes \\
   & \footnotesize{Created in Rails 1.x for Infoman Inc., as detailed above.} \\
  \multicolumn{2}{c}{} \\
  \textsc{\href{http://www.laptop.org}{OLPC}} & One Laptop Per Child \\
   & \footnotesize{Contributed specifications and prototype of Develop activity, a component intended to enable children in the OLPC program to modify and create Activity software.} \\
  \multicolumn{2}{c}{} \\
  \textsc{\href{http://www.srb2.org}{SRB2}} & DOOM-based game with a classic platformer twist \\
   & \footnotesize{Contributed some platform support code, bug fixes, and hosting of online development facilities including issue tracking and source code repository.} \\
  \multicolumn{2}{c}{} \\
  \textsc{\href{http://www.oclug.on.ca}{OCLUG}} & Ottawa Canada Linux Users' Group \\
   & \footnotesize{Served on board of directors in 2004.}
\end{longtable}

\end{document}
